DNSKEY Management

### 2012-12-05 paper/paper.tex
minor corrections.

\subsection{Operations}
In the following, every necessary operation for key management in
DNSSEC is described as a reminder to the reader. This is by no means
intended to give an introduction to DNSSEC but rather to remind the
reader about specific details particularly relevant to this paper.

@@

\section{Operations\wbjp}
This section covers the issues and quirks related to the management of DNSSEC.
\subsection{3Rs}
%% Talk about EPP or push burden to Case-Study
Regarding the management of the Internet namespace, three entities can generally be considered:

\begin{itemize}
\item a registry;
\item a registrant;
\item a registrar.
\end{itemize}

>>>>

\subsection{Operations\wbts}
In the following, every necessary operation for key management in
DNSSEC is described as a reminder to the reader. This is by no means
intended to give an introduction to DNSSEC but rather to remind the
reader about specific details particularly relevant to this paper.

@@

\section{Operations\wbjp}
This section covers the issues and quirks related to the management of DNSSEC.
\subsection{3Rs}
%% Talk about EPP or push burden to Case-Study
Regarding the management of the Internet namespace, three entities can generally be considered, namely:

\begin{itemize}
\item \textbf{R}egistries;
\item \textbf{R}egistrants;
\item \textbf{R}egistrars.
\end{itemize}
